Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-03-18 analysis/paper/paper.Rmd
survey_dates.R looks at the first and last days of target species sightings during surveys to account for possible phenology changes. survey_duration.R attempts to partially examine survey effort by looking at boxplots of duration in each site by year.

@@

```{r EDA_SurveyTiming, eval=TRUE, cache = FALSE, include = FALSE}
# dotplot of survey times by year
source("../scripts/survey_timing_EDA.R", echo=FALSE)

@@

print(Plot1)
```

@@

@@

>>>>

```{r SurveyEffort, eval=TRUE, cache = FALSE, include = FALSE}
#source("../scripts/survey_duration.R", echo=FALSE)
```

```{r Fig-SurveyEffort, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap=""}
#print(plot_duration)
```

@@

```{r EDA_SurveyTiming, eval=TRUE, cache = FALSE, include = FALSE}
# dotplot of survey times by year
#source("../scripts/survey_timing_EDA.R", echo=FALSE)

@@

@@

```{r SurveyDates, eval=TRUE, cache = FALSE, include = FALSE}
# scatterplot of species' first and last sightings
source("../scripts/survey_dates.R", echo=FALSE)
```

```{r Fig-SurveyDates1, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="The first sighting of each species each year."}
print(plot_timing_1)
```

@@

```{r Fig-SurveyDates2, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="The last sighting of each species each year."}
print(plot_timing_2)
```
